---
title: "Final Project"
author: "Sony Nghiem"
date: "December 2, 2016"
output: pdf_document
---
Both datasets come from UCI Machine Learning Repository
https://archive.ics.uci.edu/ml/datasets/Dow+Jones+Index

```{r }
dat = read.csv("datasets/dow_jones_index.data", header=TRUE)
summary(dat)
```
The first dataset is dat$open, which reflects the price of the stock at the beginning of the week.
```{r}
open = dat$open
plot(open)
acf(open) 
Box.test(x=open, lag=13, type="Ljung-Box")
```
Due to the small p-value, I could reject that the data is indipendenly distributed. In other words, there is a serial correlation of <=13 lags.

```{r}
fitAR1 = arima(open, order = c(1,0,0)) 
fitAR1
```
Here I got AR(1)
```{r}
acf(fitAR1$residuals)
Box.test(fitAR1$resid,lag=4,type="Ljung-Box",fitdf=1)
```
Now I decide to try auto arima to fit the data automatically with max p and q.
```{r}
fit1=auto.arima(open,max.p=20,max.q=0,max.d=0,max.P=0,max.D=0,max.Q=0,ic="aic")
fit1
acf(fit1$residuals)
Box.test(fit1$resid,lag=4,type="Ljung-Box",fitdf=1)
```
There is a bit improvement. So I got ARIMA(2,0,0) for this dataset.

For the second dataset from the Dow Jones, I decide to chose volume.
```{r}
volume=log(dat$volume)
plot(volume)
acf(volume)
fit2 = auto.arima(volume,max.p=20,max.q=0,max.d=0,max.P=0,max.D=0,max.Q=0,ic="aic")
fit2
```
Here we have ARIMA(2,0,0) also.
```{r}
Box.test(fit2$residuals,lag=10,type="Ljung-Box",fitdf=1)
```
I am going to try GARCH model.
```{r}
library(fGarch)
fit2=garchFit(formula=~arma(2,0)+garch(1,1),data=volume)
resid = residuals(fit2)
acf(resid)
Box.test(resid,lag=10,type="Ljung-Box",fitdf=1)
```
There is no much improvement in p-value I guess. I will rest it here and move on to the next part is fitting the multivariate parametric to them jointly.